% Autogenerated translation of about.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\renewcommand*\familydefault{\sfdefault}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}
\Large

+++

\chapter*{About/Biography widget.}

widget = "about"
active = true
date = 2016-04-20T00:00:00

\chapter*{Order that this section will appear in.}

weight = 5

\chapter*{List your academic interests.}

[interests]
  interests = [
    "Voting Behaviour",
    "Public Opinion", 
    "Populism",
    "Democratic representation", 
    "Campaign and party finance",
    "Text Analysis",
    "Big Data", 
    "Machine Learning"
  ]

\chapter*{List your qualifications (such as academic degrees).}

[[education.courses]]
  course = "PhD Candidate"
  institution = " KU Leuven, Leuven, Belgium"

[[education.courses]]
  course = "MSc in Statistics"
  institution = " KU Leuven, Leuven, Belgium"

[[education.courses]]
  course = "MA in Political Science"
  institution = "Central European University, Budapest, Hungary"
  year = 2018

[[education.courses]]
  course = "BA in Political Science, International Relations, Public Administration"
  institution = "University of Padua, Padua, Italy"
  year = 2015 

+++

\chapter*{Biography}

I am a PhD candidate at the the \href{https://soc.kuleuven.be/ceso/ispo}{Institute for Social and Political Opinion Research (ISPO)}, KU Leuven, Belgium. My PhD is on political radicalism and belief systems, views on Western society, conditionality of liberal values, and polarisation. 

More generally, my research interests are mostly within the filed of voting behaviour, party finance, and political communication. Methods wise, I am particularly interested in conjoint analysis, matching techniques graphical causal models, machine learning algorithms, text analysis, and big data. 

I am a member of the survey and experimental teams of \href{http://www.teampopulism.com/}{Team Populism}, a research group that brings together renowned scholars from Europe and the Americas to study the causes and consequences of populism.

Concerning the private sector, I am an currently external consultant and analyst for \href{http://www.zkanalytics.com/}{ZK Analytics} and for the \href{https://ecpr.eu/Events/EventTypeDetails.aspx?EventTypeID=5}{European Consortium for Political Research (Methods Schools)}. 

I love cooking, films, games, reading about tech stuff, and programming. Huge Linux/Unix fan boy.

\end{document}
