---
title:  |
        |Propensity Score Matching 
        |LAB Session
author: Alberto Stefanelli and Prof. Sharon Gilad 
# date: "`r Sys.Date()`"
# fontsize: 10pt 
# bibliography: /Users/serg/gdrive/academia/library.bib
# link-citations: yes
# linkcolor: blue
output: html_document
# header-includes:
#   - \usepackage{booktabs}
#   - \usepackage{float}
#   - \usepackage{pdflscape}
#   - \usepackage{dcolumn}
#   #- \DeclareUnicodeCharacter{301}{-}
#   - \widowpenalties 1 150
#   - \newcommand{\CI}{\mathrel{\perp\mspace{-10mu}\perp}}


---

# Setting up R 

## Why R 

- Free and open source (think of science in developing countries)
- Good online-documentation (much better than some commercial software such as Mplus)
- Lively community of users (forums etc.)
- Visualization capabilities (ggplot ...)
- Cooperates with other programs and programming language (e.g. Python, )
- Popularity (See popularity statistics on books, blogs, forums)
- RStudio as powerful integrated development environment (IDE) for R
- Evolves into a scientific work suite optimizing workflow (replication, reproducability etc.)
- Institutions/people (Gary King, Andrew Gelman etc.)
- Economic power (Revolution Analytics, Microsoft R Open)

## Where to study it 

- If you haven’t used R sofar it’s necessary that you learn some basics in R. 
- Data Camp (free trial but it is commercial) 
- Try R: A short interactive intro to the language can be found here: http://tryr.codeschool.com/
- Swirl: Learn R interactively within R itself: http://swirlstats.com/
- Akos Mate ECPR R basic for the next 2 months https://github.com/aakosm/R_Basics_ECPR

## Install R on your Machine 

Below some notes on the installation and setup of R and relevant packages on your own computer:

- Install Rtools for Windows machines from CRAN (https://cran.r-project.org/bin/windows/Rtools/). 
- If you are using OS X, you will need to to install XCode, available for free from the App Store. This will install a compiler (if you don’t have a compiler installed) which will be needed when installing packages from GitHub that require compilation from C++ source code.
- Install the latest version of R from CRAN (https://cran.r-project.org/).
- Install the latest version of RStudio (https://www.rstudio.com/products/RStudio/). RStudio is the editor we’ll rely on, i.e. we’ll write code in RStudio which is subsequently sent to and run within R.
- Install the latest versions of various packages that we need. You can also update your packages by running “update.packages(ask = FALSE)” in the R commandline.


## Set up the Environment on your local machine 

- Once R-Studio is installed copy and paste the following code
- Be sure everything run smoothly 
- Try to familiarize with R if needed 
- If you are not able to figure it out you can create an account on https://rstudio.cloud/
  - It is R in the cloud (Virtual Machine)
  - It usually resolves most of the incompatibilities 
- If you are still not able to run R and R Studio
  - We will figure it out in class ;)

  
```{r, echo=T, message=FALSE, warning=FALSE,cache=F}

# A function to install the required packages
# you don't need to understand what it does
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE,repos = c(
  CRAN = 'https://cran.rstudio.com'
  #CRANextra = 'https://macos.rbind.io'
)
      )
  sapply(pkg, require, character.only = TRUE)
}


packages_needed <- c("foreign", 
                     "readr",
                     "plyr",
                     "dplyr",
                     "tidyr",
                     "tibble", 
                     "knitr",
                     "printr",
                     "stargazer",
                     "ggplot2",
                     "MatchIt",
                     "rmarkdown",
                     "repmis")

ipak(packages_needed)
```


```{r, echo=T, message=FALSE, warning=FALSE}
  # Data import
    library(foreign)
    library(haven)
    library(readr)

  # Data management
    library(plyr)
    library(dplyr)
    library(tidyr)
    library(tibble)
    library(reshape2)
    library(tidyselect)
    library(knitr)
    library(repmis)
  # Visualization 
    library(ggplot2)
    library(stargazer)
  # Report 
    library(report)
  # Matching 
    library(MatchIt)
```
